Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-03-28 paper/main.tex
add authors
sync with iridia master, update acks

\begin{document}
\title{Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems}
% Double-blind
\author{Double-blind}
% \authornote{Dr.~Trovato insisted his name be first.}
% \orcid{1234-5678-9012}
% \affiliation{%
%   \institution{Institute for Clarity in Documentation}
%   \streetaddress{P.O. Box 1212}
%   \city{Dublin} 
%   \state{Ohio} 
%   \postcode{43017-6221}
% }
% \email{trovato@corporation.com}

% \author{Ekhiñe Irurozki\inst{1} \and Manuel López-Ibáñez\inst{2}\orcidID{0000-0001-9974-1295}}
% \institute{
%    Basque Center for Applied Mathematics\\
%    \email{eirurozki@bcamath.org}
%    \and
%    University of Málaga, Málaga, Spain\\
%    \email{manuel.lopez-ibanez@uma.es}
%  }
%    \renewcommand{\shortauthors}{B. Trovato et al.}
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in
%150--250 words.
  Expensive black-box combinatorial optimization problems arise in practice
  when the objective function is evaluated by means of a simulator or a
  real-world experiment. Since each fitness evaluation is expensive in terms of
  time or resources, the number of possible evaluations is typically several
  orders of magnitude smaller than in non-expensive problems. Classical
  optimization methods are not useful in this scenario.
  In this paper, we propose and analyze UMM, an estimation-of-distribution
  (EDA) algorithm based on a Mallows probabilistic model and unbalanced rank
  aggregation (uBorda).
  Experimental results on black-box versions of LOP and PFSP show that UMM
  outperforms the solutions obtained by CEGO, a Bayesian optimization algorithm
  for combinatorial optimization. Nevertheless, a slight modification to CEGO,
  based on the different interpretations for rankings and orderings,
  significantly improves its performance, thus producing solutions that are
  slightly better than those of UMM and dramatically better than the original
  version.  Another benefit of UMM is that its computational complexity
  increases linearly with both the number of function evaluations and the
  permutation size, which results in computation times an order of magnitude
  shorter than CEGO, making it specially useful when both computation time and
  number of evaluations are limited.
  \sloppy
\end{abstract}
%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002950.10003624.10003625.10003630</concept_id>
<concept_desc>Mathematics of computing~Combinatorial optimization</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10010061.10011795</concept_id>
<concept_desc>Theory of computation~Random search heuristics</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

@@

\myparagraph{Reproducibility} Source code, datasets and scripts necessary to reproduce the results are available at \supplement.
%  \vspace*{-1em}
%\begin{acks}
%% MANUEL: Blind, so no acknowledgments yet.
%\paragraph*{Acknowledgements.} Blind
% M.\@ L\'opez-Ib\'a\~nez is a ``Beatriz Galindo'' Senior Distinguished Researcher (BEAGAL 18/00053) funded by the Ministry of Science and Innovation of the Spanish Government.
%
%\manuel{}{: We should also thank the COST ACTION: Ask Carlos?} \ekhine{}{Sure!, esto no habra q ponerlo aun por ser blind, no?}
%Thanks to: Hao Wang (Leiden University) for pointing us to the arguments of
%\citep{EriPeaGar2019scalable}; Thomas Stützle (Université libre de Bruxelles) for suggesting works
%about differences between QAPLIB instances; and Ahmed Boujaada for the experimental support. 
  % supported by the \grantsponsor{GS501100001809}{National Natural
  %   Science Foundation of
  %   China}{http://dx.doi.org/10.13039/501100001809} under Grant
  % No.:~\grantnum{GS501100001809}{61273304}
  % and~\grantnum[http://www.nnsf.cn/youngscientists]{GS501100001809}{Young
  %   Scientists' Support Program}.
%\end{acks}

>>>>

\begin{document}
\title{Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems}
% Double-blind
%\author{Double-blind}
% \authornote{Dr.~Trovato insisted his name be first.}
% \orcid{1234-5678-9012}
% \affiliation{%
%   \institution{Institute for Clarity in Documentation}
%   \streetaddress{P.O. Box 1212}
%   \city{Dublin} 
%   \state{Ohio} 
%   \postcode{43017-6221}
% }
% \email{trovato@corporation.com}

\author{Ekhiñe Irurozki}
\affiliation{
  \institution{Basque Center for Applied Mathematics}
}
  \email{eirurozki@bcamath.org}

\author{Manuel López-Ibáñez}
\orcid{0000-0001-9974-1295}
\affiliation{
  \institution{University of Málaga}
  \city{Málaga}
  \state{Spain}
}
\email{manuel.lopez-ibanez@uma.es}

%    \renewcommand{\shortauthors}{B. Trovato et al.}
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in
%150--250 words.
  Expensive black-box combinatorial optimization problems arise in practice
  when the objective function is evaluated by means of a simulator or a
  real-world experiment. Since each fitness evaluation is expensive in terms of
  time or resources, the number of possible evaluations is typically several
  orders of magnitude smaller than in non-expensive problems. Classical
  optimization methods are not useful in this scenario.
  In this paper, we propose and analyze UMM, an estimation-of-distribution
  (EDA) algorithm based on a Mallows probabilistic model and unbalanced rank
  aggregation (uBorda).
  Experimental results on black-box versions of LOP and PFSP show that UMM
  outperforms the solutions obtained by CEGO, a Bayesian optimization algorithm
  for combinatorial optimization. Nevertheless, a slight modification to CEGO,
  based on the different interpretations for rankings and orderings,
  significantly improves its performance, thus producing solutions that are
  slightly better than those of UMM and dramatically better than the original
  version.  Another benefit of UMM is that its computational complexity
  increases linearly with both the number of function evaluations and the
  permutation size, which results in computation times an order of magnitude
  shorter than CEGO, making it specially useful when both computation time and
  number of evaluations are limited.
  \sloppy
\end{abstract}
%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002950.10003624.10003625.10003630</concept_id>
<concept_desc>Mathematics of computing~Combinatorial optimization</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003752.10010061.10011795</concept_id>
<concept_desc>Theory of computation~Random search heuristics</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

@@

\myparagraph{Reproducibility} Source code, datasets and scripts necessary to reproduce the results are available at \supplement.
%  \vspace*{-1em}
\begin{acks}
%\paragraph*{Acknowledgements.} Blind
We would like to thank Hao Wang (Leiden University) for pointing us to the arguments of
\citep{EriPeaGar2019scalable}.
%
\manuel{}{: We should also thank the COST ACTION}
%
M.\@ L\'opez-Ib\'a\~nez is a ``Beatriz Galindo'' Senior Distinguished Researcher (BEAGAL 18/00053) funded by the Ministry of Science and Innovation of the Spanish Government. 
%Thomas Stützle (Université libre de Bruxelles) for suggesting works
%about differences between QAPLIB instances; and Ahmed Boujaada for the experimental support. 
  % supported by the \grantsponsor{GS501100001809}{National Natural
  %   Science Foundation of
  %   China}{http://dx.doi.org/10.13039/501100001809} under Grant
  % No.:~\grantnum{GS501100001809}{61273304}
  % and~\grantnum[http://www.nnsf.cn/youngscientists]{GS501100001809}{Young
  %   Scientists' Support Program}.
\end{acks}
